\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage[unicode, colorlinks, linkcolor=RoyalBlue, urlcolor=RoyalBlue, citecolor=RoyalBlue]{hyperref}
\definecolor{RoyalBlue}{rgb}{0.25,0.41,0.88}

% Page dimensions
\geometry{
    left=1.27cm,
    right=1.27cm,
    top=1.27cm,
    bottom=1.27cm,
}

% Footer settings
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\footnotesize Updated On: \today}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{15pt} % Add this line to set a suitable value for \footskip

\urlstyle{same}

% Text alignment
\RaggedRight{}
\setlength{\tabcolsep}{0in}

% Section title formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item[$\bullet$] \small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubheading}[5]{
    \vspace{-1pt}\item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{#4}{#1}} & #2 \\
    \textit{\small#3} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

% CV Start
\begin{document}

% Title
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textsc{\LARGE Farzana Yesmin} & \\
	Road-20, Sector-13 & Mobile: +880 1990-771124 \\
	Uttara, Dhaka & Email: \href{mailto:yesminfarzana.cse@gmail.com}{yesminfarzana.cse@gmail.com} \\
	Bangladesh & Portfolio: \href{https://portfolio-farzana-yesmin.vercel.app/}{https://portfolio-farzana-yesmin.vercel.app/} \\
\end{tabular*}

% Education
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Daffodil International University}{Dhaka, Bangladesh}
{Bachelor of Science in Computer Science and Engineering; CGPA: \textbf{3.63}}{https://daffodilvarsity.edu.bd/}{Jan. 2019 -- Dec. 2022}
\resumeSubheading
{Universiti Kebangsaan Malaysia}{Malaysia}
{Exchange Program from Erusmus Mundus Scholarship}{https://www.ukm.my/portalukm/}{Mar. 2022 -- Aug. 2022}
\resumeSubHeadingListEnd

% Experience
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{RedGreen Technology Ltd.}{Dhaka, Bangladesh}
{Jr. Software Engineer}{https://www.google.com/}{Jul. 2023 - Jun. 2024}
\resumeItemListStart
\resumeItem{Developed responsive UIs using React and Angular for seamless user experience across devices.}
\resumeItem{Collaborated with design and backend teams to implement interactive web components.}
\resumeItem{Optimized front-end code, reducing page load times through refactoring and asset management.}
\resumeItemListEnd
\resumeSubheading
{Daffodil International University}{Dhaka, Bangladesh}
{Student Associate, Dept. of International Affairs}{https://daffodilvarsity.edu.bd/}{February 2022 – May 2022}
\resumeItemListStart
\resumeItem{Assisted in organizing international exchange programs and events.}
\resumeItem{Handled administrative tasks related to student mobility and foreign collaborations.}
\resumeItem{Supported coordination between international students and the university.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{ReFactory}{}
{RedGreen Technology Ltd.}{https://www.refactory.ae/}{}
\resumeItemListStart
\resumeItem{Utilized React.js to develop dynamic and responsive user interfaces, ensuring a seamless and engaging experience for users.}
\resumeItem{Handled API integrations to fetch and display real-time data, enhancing the functionality and interactivity of the web application.}
\resumeItem{Implemented responsive design principles, optimizing the application for various devices and screen sizes, while maintaining performance and usability.}
\resumeItemListEnd
\resumeSubheading
{FruitBurst}{}
{Pet Project.}{https://farzanayesminn.github.io/FruitBrust_HTML-TailwindCSS_Responsive/}{}
\resumeItemListStart
\resumeItem{Developed a responsive website showcasing a variety of fruits, utilizing HTML and Tailwind CSS to ensure an appealing and user-friendly interface.}
\resumeItem{Implemented interactive features such as hover effects and animations, enhancing user engagement and providing a delightful browsing experience.}
\resumeItem{Optimized the website for mobile devices, ensuring seamless functionality across various screen sizes and improving accessibility for all users.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Publications}
\textbf{Yesmin, F.}, Rahman, M., Saifuzzaman, M., \& Moon, N. N. (2022). Pandemic Effect on Education System Among University Students. In International Conference on Deep Learning, Artificial Intelligence and Robotics (pp. 157-168). Springer, Cham.

% Programming Skills
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
      \textbf{Core Skills:} Frontend Development, Responsive Web Design, UI/UX Design \\
      \textbf{Programming Languages:} JavaScript, HTML, CSS \\
      \textbf{Frameworks/Libraries:} React, Tailwind CSS, Bootstrap \\
      \textbf{Technical Tools:} Git, Figma, Chrome DevTools \\
      \textbf{Backend Knowledge:} Basic understanding of Node.js, REST API
}
\resumeSubHeadingListEnd

\end{document}